YOSHIHIKO KUNISATO, Ph.D.

### 2018-01-06 index.Rmd
メールアドレスの修正

### Contact
#### Yoshihiko Kunisato, Ph.D.
#### Department of Psychology, Senshu University
#### ADRESS: 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, Kanagawa 214-8580, Japan
#### E-MAIL: ykunisato<at>psy.senshu-u.ac.jp

>>>>

### Contact
#### Yoshihiko Kunisato, Ph.D.
#### Department of Psychology, Senshu University
#### ADRESS: 2-1-1, Higashimita, Tama-ku, Kawasaki-shi, Kanagawa 214-8580, Japan
#### E-MAIL:ykunisato (at sign) psy.senshu-u.ac.jp

### 2018-01-06 yoshihiko-kunisato.Rmd
メールアドレスの修正

## PERSONAL INFORMATION
####  Yoshihiko Kunisato
####  Associate Professor of Clinical Psychology
####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
####  DATE OF BIRTH: November 11, 1983
####  PLACE OF BIRTH: Hyougo Japan
####  CITIZENSHIP: Japanese
####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
####  E-MAIL: ykunisato<at>psy.senshu-u.ac.jp
####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)
####  [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)

>>>>

## PERSONAL INFORMATION
####  Yoshihiko Kunisato
####  Associate Professor of Clinical Psychology
####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
####  DATE OF BIRTH: November 11, 1983
####  PLACE OF BIRTH: Hyougo Japan
####  CITIZENSHIP: Japanese
####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
####  E-MAIL: ykunisato (at sign) psy.senshu-u.ac.jp
####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)
####  [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)
